Final Report: The need for mental health outreach in the workplace

### 2018-12-14 Final /FinalReport.Rmd
Final report changes
Pushing individual ontribution of mona
As her github stopped working, it was pushed from my system

---
title: "Final Report Semester Project"
output:
  word_document: default
---

@@

Monalisa -

>>>>

---
title: "Final Report: The need for mental health outreach in the workplace"
output:
  word_document: default
---

@@

Monalisa - In the initial stage, I collaborated with the team to do prelimnary research in the area of mental health and create the work plan. I came up with about 9 research questions that we could analyze using the dataset. (We all did some brainstorming with all suggested questions and shortlisted 15 questions for the analysis). For the data cleaning phase, I examined and cleaned 10 variables. For the R Script, I collaborated with the team to understand what kind of tests we can run with the variables and what questions can be answered by doing so. I was assigned 5 questions that helped gain insights into the number of employers in the dataset who provided mental health benefits to the employees, if they formally discussed these policies and questions that answered employee perception of negative consequences of discussing mental health at previous and current workplace. I did statistical tests (Chi-squared and Crammer's V) to conclude that a relationship exists between the two variables. As all my variables were categorical, I used barplots, ggplots and Chi-squared tests to perform visualizations and to test relationships respectively. For the presentation, I again collaborated with the team and created slides for my part of the analysis. Lastly, I cleaned my part of the code based on the feedback received.
